\LARGE \bf Multi-Armed Bandit Models for 2D Grasp Planning with Uncertainty

### 2015-06-15 paper.tex
added Ken's feedback, fixed Fig. 5

The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore. However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity~\cite{goetschalckx2011continuous}. Chapelle et al. demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case~\cite{chapelle2011empirical}. Agrawal et al. recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear for $k$-arms and logarithmic in the case of $2$ arms ~\cite{agrawal2011analysis}.

>>>>

The intuition for Thompson sampling is that the random samples of $p_{k,t}$ allow the method to explore. However, as more samples are received the method focuses on promising arms, since the Beta distributions approach delta distributions as number of samples drawn goes towards infinity~\cite{agrawal2011analysis}. Chapelle et al. demonstrated empirically that Thompson sampling achieved lower cumulative regret than traditional bandit algorithms like UCB for the Beta-Bernoulli case~\cite{chapelle2011empirical}. Agrawal et al. recently proved an upper bound on the asymptotic complexity of  cumulative regret for  Thompson sampling that is sub-linear for $k$-arms and logarithmic in the case of $2$ arms ~\cite{agrawal2011analysis}.
